### 2010-02-17 trunk/deliverables/D5_2_2/fast_d5_2_2.tex
final version of 5.2.2
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@565 d8b0c59b-6544-0410-94d9-83a5658a058e

\usepackage{inputenc}
\usepackage{lastpage}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage[pdfborder={0 0 0}]{hyperref}		% turn on when latex is used (not miktec)
\usepackage{url} % LEO: urls \url{}
\usepackage{verbatim} % code and comment
\usepackage{longtable}
\usepackage{xspace}   % whitespace after a macro if no punctuation after the macro
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable}
\usepackage{array}
\usepackage{amssymb}
\parindent0pt

\newcommand\deliverableNumber{D5.1.2}
\newcommand\deliverableTitle{User Manual of the FAST Catalogue}
\newcommand\deliverableTitleShort{Catalogue User Manual}
\newcommand\workpackageNumber{5}
\newcommand\workpackageTitle{Semantic catalogue of screen-flow resources and back-end Web Services}
\newcommand\authorOne{Ismael Rivera, NUIG}
\newcommand\authorTwo{Author 2}
\newcommand\authorThree{Author 3}
\newcommand\authorFour{Author 4}
\newtheorem{example}{\emph{Example}}

@@

%\begin{minipage}[p]{15cm}
	\begin{center}
		\includegraphics{images/FAST_logo}\\
		\vspace{1cm}
		{\LARGE{\sffamily \emph{FAST AND ADVANCED STORYBOARD TOOLS}}}\\
		\vspace{0.5cm}
		{\LARGE \sffamily \emph{FP7-ICT-2007-1-216048}}\\
		\vspace{0.5cm}
		{\LARGE \sffamily \emph{http://fast.morfeo-project.eu}}\\
		\vspace{4cm}
		{\LARGE \sffamily \textbf{Deliverable \deliverableNumber}}\\
		\vspace{0.5cm}
		{\LARGE \sffamily \textbf{\deliverableTitle}}\\
		\vspace{2cm}
		{\large \sffamily \authorOne}\\
		\vspace{0.5cm}
		\vfill
		{\large \sffamily Date: 25/01/2010}\\
		\vspace{1cm}
		{\sffamily FAST is partially funded by the E.C. (grant code: FP7-ICT-2007-1-216048).}

@@

\begin{small}
\begin{tabular}{|l|l|l|p{7.5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{\textbf{Rev. No.}} &
                         \textcolor{white}{\textbf{Date}} &
                         \textcolor{white}{\textbf{Author (Partner)}} &
                         \textcolor{white}{\textbf{Change description}}\\ \hline
1.0 & 25/01/2010 & Ismael Rivera (NUIG) & First version of the deliverable \\ \hline
\end{tabular}
\end{small}

@@

The present deliverable is intented to be the developer's manual of the prototype of the semantic catalogue. That said, whoever developing a component which will interact with the catalogue will find in this document a description of its architecture, the functionality provided together with the API (Application Programming Interface), data interchange formats, code errors and exceptions as well as several examples of usage.

@@

\begin{small}
\begin{tabular}
	{| >{\columncolor{fast@lightgrey}}p{3.25cm}|p{1.4cm}|p{3.28cm}|p{1.6cm}|p{3.29cm}|}
	\hline
	\textcolor{white}{\textbf{Delivery data}} & {\textbf{Due date}} & {27/02/2010} & {\textbf{Submitted}} & {27/02/2010}\\ \hline
	\textcolor{white}{\textbf{Status}} & \multicolumn{2}{l|}{} & \multicolumn{2}{l|}{final}\\ \hline
	\textcolor{white}{\textbf{Dissemination Level}} & \multicolumn{4}{l|}{Public $\boxtimes$ / Consortium $\square$}\\ \hline
	\textcolor{white}{\textbf{Short description of contents}} & \multicolumn{4}{p{10.85cm}|}{This deliverable is the technical documentation for the prototype developed as part of the WP5. It describes the catalogue's architecture, data interchange formats, APIs and examples of how to interact with it.}\\ \hline
	\textcolor{white}{\textbf{Authors}} & \multicolumn{4}{l|}{\authorOne}\\
%	{} & \multicolumn{4}{l|}{\authorOne}\\ 
%	{} & \multicolumn{4}{l|}{\authorOne}\\ 
%	{} & \multicolumn{4}{l|}{\authorOne}\\
  \hline
	\textcolor{white}{\textbf{Deliverable Owner}} & \multicolumn{2}{l|}{NUIG} & \textbf{email} & {ismael.rivera@deri.org} \\ \cline{4-5}
	\textcolor{white}{\textbf{(Partner)}} & \multicolumn{2}{l|}{} & \textbf{phone} & {+353 91 495338} \\ \hline
	\textcolor{white}{\textbf{Keywords}} & \multicolumn{4}{p{10.85cm}|}{FAST, semantic catalogue, gadget catalogue, RDF store}\\ \hline
\end{tabular}
\end{small}

@@

\clearpage
\listoftables

\clearpage
\listoffigures

@@

\clearpage
\section{Introduction} % (fold)
\label{sec:introduction}
This section starts establishing the goal and scope of the present document, shows how it is structured and details the relation to others documents and work packages.

@@

This is an introductory manual for developers who want to adopt and use the FAST semantic catalogue. It explains the main functionalities implemented so far, an overview of its architecture and a detailed \emph{Application Programming Interface} or API of the complete set of the operations offered through a REST service.

\subsection{Structure of the document} % (fold)
\label{sub:structure_of_the_document}

The deliverable presents both the external and internal architecture in Section~\ref{sec:architecture_overview}, then in Section~\ref{sec:restful_catalogue_api} it is detailed the Catalogue API, query formats, interchange formats, error codes and so on.

@@

This should be the first version of this deliverable since in M12 the deliverable 5.1 was not scheduled. Nevertheless, last year an extra document was written as an appendix to the FAST Catalogue in order to detail and clarify technical decisions and to have a technical reference manual. Hence, the deliverable D5.2.1 will evolve to become the D5.1.2, so it will be no longer needed by itself.

There are several new sections and major changes which need to be mentioned:

\begin{itemize}
	\item Section~\ref{sec:installation_guide}. Installation Guide describes a set of steps to be followed in order to install and execute the FAST Catalogue. Also some configuration instructions are specified.
	\item Section~\ref{sub:linked_data}. Content Negotiation states how the FAST Catalogue has adopted several of the content negotiation principles.
	\item Section~\ref{sec:restful_catalogue_api}. RESTful Catalogue API has been intensively extended and modified in order to  reflect all the new functionality and how every request or response is constructed. Some of the most important features added in this iteration are:
	\begin{itemize}
		\item support for form elements, operators and back-end services (see Section ...),
		\item convenience operations for recommendation and checking satisfaction and reachability for form elements, operators and back-end services (see Section ...),
		\item and, last but not least, support for Screen planning (see Section~\ref{sub:planning}).
	\end{itemize}
	\item Several appendixes have been added with the JSON structure of every building block the Catalogue can deal with.
	\item Appendix A. Last year an evaluation to choose the best technology for the Catalogue was done. It was not included in any formal deliverable, so this year it has been documented as an appendix.
\end{itemize}

@@

\clearpage
\section{Installation Guide} % (fold)
\label{sec:installation_guide}

This section  provides instructions on how to manually install and configure the FAST Catalogue. The first part of this guide presents some requirements to be considered before the installation, then it gives broad general instructions, and the last part contains a more detailed installation notes for specific configurations.

\subsection{System Requirements} % (fold)
\label{sub:system_requirements}

In addition to the software itself, a standard FAST Catalogue installation has the following requirements:
\begin{itemize}
  \item Java\footnote{http://java.sun.com/} (version 6 or later) is required to run the software.
  \item A Java Servlet Container that supports Java Servlet API 2.4 and Java Server Pages (JSP) 2.0, or newer. We recommend using a recent, stable version of Apache Tomcat\footnote{http://tomcat.apache.org/}. At the time of writing, this is either version 5.5.x or 6.x.
\end{itemize}

In addition, there are various optional dependencies which are required if you want to use certain advanced features (see Section~\ref{sub:installation_instructions}).

% subsection system_requirements (end)

\subsection{Obtaining the FAST catalogue} % (fold)
\label{sub:obtaining_the_fast_catalogue}

It is recommended to have a Subversion client installed before you download the code (although you can theoretically download files without Subversion, this would mean tediously downloading each individual file manually). The recommended software is the official Subversion client, available from the Subversion project page\footnote{http://subversion.tigris.org/}. Note that this client uses a command-line interface, which the instructions below use. Alternatively, you can get subversioning software with a graphical user interface such as TortoiseSVN.

To download from the latest release (recommended), enter the following command from the command-line in the directory you wish to download to:
\begin{verbatim}
svn checkout https://svn.forge.morfeo-project.org/fast-fp7project/trunk/catalogue_service
\end{verbatim}

% subsection obtaining_the_fast_catalogue (end)

\subsection{Installation Instructions} % (fold)
\label{sub:installation_instructions}

Once you have got the source code, first step should be addressed is its compilation. You may manually compile the source yourself, however the FAST Catalogue comes along with a script to facilitate this task. This script has been made using a Java build tool called Ant \footnote{http://ant.apache.org/}. Hence, we recommended to get and install such a tool in order to follow the instructions below.

Now you can compile, package and run the application via:
\begin{verbatim}
ant clean
ant prepare
ant compile
\end{verbatim}

Or using a task which gather the previous three tasks and creates WAR file ready to distribute or deploy:
\begin{verbatim}
ant dist
\end{verbatim}

After executing with no errors this task, a WAR file should have been created in the /dist directory. A WAR file, which stands for  Web Application Archive, is just a JAR file used to distribute a collection of JavaServer Pages, servlets, Java classes, XML files, tag libraries and static Web pages (HTML and related files) that together constitute a Web application, in this case, the FAST Catalogue.

Note that it is also possible to get the compiled WAR file directly from the SVN server. This file can be located at \url{https://svn.forge.morfeo-project.org/fast-fp7project/distribution/catalogue}.

Then, last step is to deply the WAR file into the servlet container. If the server chosen was Apache Tomcat, the procedure for deploying a Web application is:
\begin{enumerate}
	\item Stop Tomcat.
	\item Delete existing deployment. If you have previously deployed "foo.war" in TOMCAT\_HOME/webapps, then it has been unpacked into webapps/foo/... You must delete this directory and all its contents. On Unix, this can be done with
rm -r \$TOMCAT\_HOME/webapps/foo
	\item Copy WAR file to TOMCAT\_HOME/webapps/.
	\item Start Tomcat.
\end{enumerate}

Now you have successfully built the FAST catalogue, however we highly recommend you to read Section~\ref{sub:configuration} and tune your FAST Catalogue instance.

% subsection installation_instructions (end)

\subsection{Configuration} % (fold)
\label{sub:configuration}

The following section covers the configuration options you may have to set up before start using the Catalogue. The FAST Catalogue relies on a Sesame repository for the persistent storage. Sesame repositories can be local or remote. Remote does not mean, it has to be installed in a different machine, but in a servlet container such as Apache Tomcat. The advantage of remote repositories is the possibility of accessing it via a SPARQL endpoint. These configuration aspect can be found in the file \emph{repository.properties} in the root directory where the Catalogue has been deployed.

Independently the type of repository, the parameter \emph{serverURL} needs to take the value of the URL where the FAST Catalogue instance has been deployed. If you are testing the application in your machine, it may be something like \url{http://catalogueURL/FASTCatalogue}.

Local repositories just need the parameter \emph{storageDir} pointing at a local directory, which has write permission in order to allow Sesame to create files in that directory or to delete any file in the directory. For instance:

\begin{verbatim}
storageDir=D:\\FAST\\catalogue\\repository
\end{verbatim}

Nevertheless, setting up a remote repository requires a few more steps. First the OpenRDF Sesame Server needs to be installed. The installation guide of this server is detailed in the Chapter 5 and 6 of the User Guide for Sesame 2.2 \cite{sesame2.2}. Once the Sesame server is deployed, and a repository has been created, the parameters sesameServer and repositoryID will take the values of the Sesame server URL and the repository identifier. For instance:

\begin{verbatim}
sesameServer=http://localhost:8880/openrdf-sesame
repositoryID=c2
\end{verbatim}

% subsection installation_instructions (end)

\subsection{Hello World!} % (fold)
\label{sub:hello_world}

It is recommended to check if the FAST Catalogue has been successfully installed. To do that, a simple HTTP request, using a Web browser, can be sent to the URL the Catalogue is deployed, and specifying a type of resource such as Screen. The URL would be similar to \url{http://catalogueURL/FASTCatalogue/screens}. Depending on the variant chosen, the response may be different. For JSON, the response should be \verb|[]|, but in HTML the message \verb|No screens found.| should be shown.

% subsection hello_world (end)

% section installation_guide (end)

\clearpage
\section{Architecture Overview} % (fold)
\label{sec:architecture_overview}

This section presents a technical overview of the internal catalogue's architecture and which external components will interact with it. Basically three layers can be distinguished: Presentation, Business Logic and Persistence layer (see Figure~\ref{fig:catalogue_architecture}).

\begin{figure}[htb]
\label{fig:catalogue_architecture}
\begin{center}
	\includegraphics[width=12cm]{images/catalogue_architecture}
	\caption{Catalogue's Architecture}
\end{center}
\end{figure}

The Presentation layer will be the public interface of the catalogue. The main purpose of this layer is to provide its functionality to other components within the Gadget Visual Studio. The service is offered in a REST (REpresentational State Transfer) style, making it easy to consume than other complex APIs. REST is an architectural style, not a toolkit or a standard. Even though, it makes use of standards like HTTP, URI, Resource Representations (XML, HTML, JSON, JPEG, etc.) or MIME types (text/xml, text/html, application/json, image/jpeg, etc.). Another characteristic of the REST style is its stateless assumption. The catalogue adopts this strategy; therefore every request needs a complete set of information in order to prepare the response.

As part of the Presentation layer, a SPARQL endpoint is offered using the SPARQL protocol service as defined in the SPROT \cite{sprot} specification. The SPARQL endpoint is mostly offered to enable other developers to query directly the catalogue knowledge base using SPARQL queries. This feature is supported by the Sesame RESTful HTTP interface for SPARQL Protocol for RDF.

The Business Logic layer contains all the FAST domain-specific processing. It provides functions to interact with all the elements of the domain model specified in \cite{moeller2009fast_ontology}. It processes the input from the Presentation layer, creating specific objects modelling the business logic, and vice versa. In addition it interacts with the Persistence layer in order to persist the model.

The Persistence layer provides an API which allows the Business layer to work with a standard set of objects that read and save their state to the triple store. For this reason, on top of this layer it is used RDF2Go, an abstraction over triple (and quad) stores. The RDF2Go API allows interacting with the semantic representation of the model (triples) in a generic manner, and also brings the flexibility of choosing different triple stores to persist them. The selected implementation for the triple stored is Sesame 2. Moreover, this framework is completely extensible and configurable regarding to storage mechanisms, inferencers, RDF file formats, query result formats and query languages. For the actual catalogue prototype, the storage mechanism used is the native file storage system of Sesame, the inferencer used is a subset of the RDFS entailment rules \cite{rdfsrules} following a forward-chaining policy.

% section architecture_overview (end)

\clearpage
\section{RESTful Catalogue API} % (fold)
\label{sec:restful_catalogue_api}

This section provides a high-level overview of the Catalogue API. It describes the calls or operations supported, specific parameters and responses for each operation, supported interchange formats and some examples to facilitate the understanding of the API.

\subsection{JSON Interchange Format} % (fold)
\label{sec:json_interchange_format}

The format supported, and in which they must be constructed, by every HTTP request is JSON\footnote{http://www.json.org/}. JSON is a lightweight data interchange format whose simplicity has resulted in widespread use among web developers, easy to read and write and able to using any programming language because its structures map directly to data structures used in most programming languages.

Every HTTP request should be encoded using the MIME type \texttt{application/json} and the charset \texttt{UTF-8}.

The following is an example of a Find \& Check request:

\singlespacing
\begin{verbatim}
{
  "canvas": [
    { "uri": "http://catalogueURL/catalogue/screens/238" },
    { "uri": "http://catalogueURL/catalogue/screens/323" }
  ],
  "elements": [
    { "uri": "http://catalogueURL/catalogue/screens/636" }
  ],
  "domainContext": {
    "tags": [
      {
        "label": { "en-GB": "Amazon" },
        "means": "http://dbpedia.org/page/Amazon.com"
      }
    ],
    "user": "irivera",
  },
  "criterion": "reachability"
}
\end{verbatim}
\doublespacing

\subsubsection{Internationalisation I18n} % (fold)

In order to offers an adaptable solution to various languages and regions without major engineering changes, internationalisation is considered from an early stage in the catalogue development. Underlying representation technologies used to develop the catalogue (RDF/XML and JSON) allow to implement this feature. This feature is implemented by the addition of a language tag to every 'string' desired. The specification of this language tag is composed by the language code and the country code, following the ISO 639\footnote{http://ftp.ics.uci.edu/pub/ietf/http/related/iso639.txt} for languages and the ISO 3166\footnote{http://userpage.chemie.fu-berlin.de/diverse/doc/ISO\_3166.html} for countries. The following example illustrates how to use it properly in both formats.

\singlespacing
\begin{verbatim}
{
  "label": {
    "en-GB": "Simple Example",
    "es-ES": "Ejemplo Sencillo",
    "de-DE": "Einfaches Beispiel"
  },
  "description": {
    "en-GB": "This is a simple example of a screen",
    "es-ES": "Esto es un ejemplo sencillo de pantalla",
    "de-DE": "Dies ist ein einfaches Beispiel für einen Bildschirm"
  },
}
\end{verbatim}
\doublespacing

\singlespacing
\begin{verbatim}
<rdf:Description rdf:about="http://www.morfeoproject.eu/fast/fco#ExampleScreen">
  <rdf:type rdf:resource="http://www.morfeoproject.eu/fast/fco#Screen"/>
  <rdfs:label xml:lang="en-GB">Simple Example</rdfs:label>
  <rdfs:label xml:lang="es-ES">Ejemplo Sencillo</rdfs:label>
  <rdfs:label xml:lang="de-DE">Einfaches Beispiel</rdfs:label>
  <description
    xmlns="http://purl.org/dc/terms/"
    xml:lang="en-GB">This is a simple example of a screen</description>
  <description
    xmlns="http://purl.org/dc/terms/"
    xml:lang="es-ES">Esto es un ejemplo sencillo de pantalla</description>
  <description
    xmlns="http://purl.org/dc/terms/"
    xml:lang="de-DE">Dies ist ein einfaches Beispiel für einen Bildschirm</description>
</rdf:Description>
\end{verbatim}
\doublespacing

Until now, using internationalisation is allowed for the label and the description of a screen, but in the near future, more attributes will benefit from this feature.

% subsection json_interchange_format (end)

\subsection{Linked Data} % (fold)
\label{sub:linked_data}

Apart from serving as the back-end system for the Gadget Visual Storyboard or GVS, the catalogue publishes all FAST building blocks as linked data following the four rules or principles dictated in \cite{bernersLee2006linkedData}. Hence, building blocks are identified by URIs, concretely HTTP URIs so anyone can look them up. The data obtained for these building blocks is served in different standard formats such as JSON (GVS communication), RDF/XML, Turtle, or even HTML+RDFa as a human-readable version. And as the forth rule states, these building blocks links to other resources on the web. Moreover, principles and best practices from \cite{berrueta2008} and \cite{sauermann2008cool_uris} have been followed for the publication and identification of the building blocks. The mechanism to allow its publication/identification in different formats is called Content Negotiation.

Before any major details about how content negotiation is addressed by the catalogue, a few concepts need to be understood. First of all, say a URI is not a file name. It is common to see a URI as the location for a file, but a URI or Universal Resource Identifier is not a URL: it is not a file name or location, it is an identifier (or a reference) to a resource. Then by dereferencing a URI the actual resource can be retrieved. Let's see a request to retrieve the resource "Screen 123" is sent to the server. The resource is just a piece of information, however the server will answer an HTML document with a text describing the screen or an image representing it. On the Web, these equivalent representations of a resource are called variants, and content negotiation is the mechanism used to determine which of the representations of most appropiate for a given request.

\begin{figure}[htb]
\label{fig:content_negotiation}
\begin{center}
	\includegraphics[width=12cm]{images/content_negotiation}
	\caption{Content Negotiation}
\end{center}
\end{figure}

In summary, the basic idea of content negotiation, as stated in the \cite{http1.1}, is to serve the best variant for a resource, taking into account what variants are available, what variants the server may prefer to serve, what the client can accept, and with which preferences: in HTTP, this is done by the client which may send, in its request, Accept headers (Accept, Accept-Language and Accept-Encoding), to communicate its capabilities and preferences in Format, Language and Encoding, respectively.

In fact, what the catalogue really does is "format negotiation" since the alternate representationos are just based on the selection of the media type, through the \emph{Accept} header, but does not consider different languages or encoding types. The formats supported are JSON, RDF/XML, Turtle and HTML+RDFa. Even though the \emph{Accept} header is desired, these different representations can be retrieved by adding the format at the end of the resource URI. For instance, to get the RDF representation of the screen 457, performing a GET HTTP request to <catalogue\_url>/screens/457.rdf will serve the information in RDF/XML.

Lastly, content negotiation needs to identify which player is going to take the lead on it. There are two kinds of content negotiation which are possible in HTTP: server-driven and agent-driven negotiation. The approach followed by the catalogue is agent-driven negotiation, hence selecting a specific representation for a resource is responsibility of the user agent. If none is specified, by default, the server will choose the JSON representation.

% subsection content_negotiation (end)

\subsection{API Calls} % (fold)
\label{sub:api_calls}

This section contains detailed descriptions of the interface provided by the catalogue via REST services, detailing request parameters, response elements, any special errors and examples of requests and responses. The URL format is also specified for each operation, where 'catalogueURL' has to be replaced for the real URL the service is installed (e.g. http://demo.fast.morfeo-project.org/catalogue).

\subsubsection{CRUD operations} % (fold)

Any building block within the Catalogue is a resource in terms of REST philosophy, hence it can be created, retrieved, modified or deleted, using a certaing URL and a specific HTTP method for every operation. Two concepts have to be defined: \emph{collection}, as a set of resources which access URI is http://catalogueURL/<type>/ where catalogueURL is the specific URL where the Catalogue server is installed and <type> is the plural of the name of the building block (e.g. screens, services), and \emph{member} of the collection, in other words, the building block itself, which access URI is http://catalogueURL/<type>/<id> where the <id> has to be replaced by the identifier of a specific building block. The details of the operations and which HTTP verb has to be used can be found in the Table~\ref{tab:crud_operations}.

\begin{table}[htb]
\caption{CRUD operations}
\label{tab:crud_operations}
\begin{center}
\begin{tabular}{|p{2.5cm}|p{2.5cm}|p{3.5cm}|p{5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{Resource} &
                         \textcolor{white}{HTTP method} &
                         \textcolor{white}{HTTP body} &
                         \textcolor{white}{Description}\\ \hline
Collection URI & GET & N/A & \textbf{List} the members of the collection.\\ \hline
Collection URI & PUT & N/A & Not used.\\ \hline
Collection URI & POST & JSON representation of the building block & \textbf{Create} a new entry in the collection where the URI is assigned automatically by the collection. The URI created is returned by this operation.\\ \hline
Collection URI & DELETE & N/A & Not used.\\ \hline
Member URI & GET & N/A & \textbf{Retrieve} the addressed member of the collection.\\ \hline
Member URI & PUT & JSON representation of the building block & \textbf{Update} the addressed member of the collection or create it with a defined URI.\\ \hline
Member URI & POST & N/A & Not used. \\ \hline
Member URI & DELETE & N/A & \textbf{Delete} the addressed member of the collection.\\ \hline
\end{tabular}
\end{center}
\end{table}

The JSON structure for create any building bock can be found in the appendixes. All of them are composed of a common structure which can be found in Section Appendix B, and some specific information depending on the type. Screen-flows are defined in Appendix C, screens in Appendix D and forms, operators and back-end services share the same structure detailed in Appendix E. However, a few examples of request and responses are shown in order to clarify how the request are constructed and sent, and how the responses look like.

To create a new screen, a POST request is send to the catalogue server, concretely to http://catalogueURL/screens, including the JSON representation of the screen in the body of the request:

\singlespacing
\begin{verbatim}
{
  "code": "http://demo.fast.morfeo-project.org/code/amazonList.js",
  "creationDate": "2010-01-26T17:01:13+0000",
  "creator": "irivera",
  "description": {"en-gb": "Please fill the description..."},
  "homepage": "http://fast.morfeo-project.eu/",
  "icon": "http://demo.fast.morfeo-project.org/images/amazonList.png",
  "id": "28",
  "label": {"en-gb": "Amazon Product List"},
  "name": "ProductList",
  "postconditions": [
    [
      {
        "id": "item",
        "label": { "en-gb": "An item" },
        "pattern": "?I 
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#Item",
        "positive": "true"
      }
    ]
  ],
  "preconditions": [
    [
      {
        "id": "filter",
        "label": { "en-gb": "A search criteria" },
        "pattern": "?F
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#SearchCriteria",
        "positive": "true"
      }
    ]
  ],
  "rights": "http://creativecommons.org/",
  "screenshot": "http://demo.fast.morfeo-project.org/images/amazonProductList.png",
  "tags": [{"label": {"en-gb": "amazon"}}],
  "version": "0.1"
}
\end{verbatim}
\doublespacing

The URI of the screen is created using the id specified in the JSON request. So, the response for this operation is:

\singlespacing
\begin{verbatim}
{
  "code": "http://demo.fast.morfeo-project.org/code/amazonList.js",
  "creationDate": "2010-01-26T17:01:13+0000",
  "creator": "irivera",
  "description": {"en-gb": "Please fill the description..."},
  "homepage": "http://fast.morfeo-project.eu/",
  "icon": "http://demo.fast.morfeo-project.org/images/amazonList.png",
  "id": "28",
  "label": {"en-gb": "Prueba1"},
  "name": "ProductList",
  "postconditions": [
    [
      {
        "id": "item",
        "label": { "en-gb": "An item" },
        "pattern": "?I
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#Item",
        "positive": "true"
      }
    ]
  ],
  "preconditions": [
    [
      {
        "id": "filter",
        "label": { "en-gb": "A search criteria" },
        "pattern": "?F
                    http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                    http://aws.amazon.com/AWSECommerceService#SearchCriteria",
        "positive": "true"
      }
    ]
  ],
  "rights": "http://creativecommons.org/",
  "screenshot": "http://demo.fast.morfeo-project.org/images/amazonProductList.png",
  "tags": [{"label": {"en-gb": "amazon"}}],
  "type": "screen",
  "uri": "http://catalogueURL/catalogue/screens/28",
  "version": "0.1"
}
\end{verbatim}
\doublespacing

To obtain all the screens stored in the catalogue a HTTP GET request is sent to the Collection URI and the response may be something like this:

\singlespacing
\begin{verbatim}
[
  {
    "code": "http://demo.fast.morfeo-project.org/code/amazonList.js",
    "creationDate": "2010-01-26T17:01:13+0000",
    "creator": "irivera",
    "description": {"en-gb": "Please fill the description..."},
    "homepage": "http://fast.morfeo-project.eu/",
    "icon": "http://demo.fast.morfeo-project.org/images/amazonList.png",
    "id": "28",
    "label": {"en-gb": "Prueba1"},
    "name": "ProductList",
    "postconditions": [
      [
        {
          "id": "item",
          "label": { "en-gb": "An item" },
          "pattern": "?I
                      http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                      http://aws.amazon.com/AWSECommerceService#Item",
          "positive": "true"
        }
      ]
    ],
    "preconditions": [
      [
        {
          "id": "filter",
          "label": { "en-gb": "A search criteria" },
          "pattern": "?F
                      http://www.w3.org/1999/02/22-rdf-syntax-ns#type
                      http://aws.amazon.com/AWSECommerceService#SearchCriteria",
          "positive": "true"
        }
      ]
    ],
    "rights": "http://creativecommons.org/",
    "screenshot": "http://demo.fast.morfeo-project.org/images/amazonProductList.png",
    "tags": [{"label": {"en-gb": "amazon"}}],
    "type": "screen",
    "uri": "http://catalogueURL/catalogue/screens/28",
    "version": "0.1"
  },
  {
    "creationDate": "2009-02-07T09:59:52+0000",
    "creator": "fabio",
    ...,
	  "uri": "http://catalogueURL/catalogue/screens/14",
    "version": "1.0"
  },
  {
    "creationDate": "2009-02-07T09:59:52+0000",
    "creator": "javier",
    ...,
	  "uri": "http://catalogueURL/catalogue/screens/564",
    "version": "1.0"
  }
]
\end{verbatim}
\doublespacing

\subsubsection{Screen Find} % (fold)
\label{ssub:screen_find}

The find operation searches inside the catalogue for any screen which could be somehow related to the gadget the user is creating. It provides a recommended set of screens depending on the domain context, the canvas, and so on.

The specific URL to access this operation is http://catalogueURL/screens/find using HTTP POST method. From now on, the method 'find' only considers the domain context and the pre/postconditions of the screens. It will try to satisfy all the unsatisfied preconditions of a given list of screens also known as canvas. The results will be all the screens stored in the catalogue which fulfil some of these preconditions, and are tagged with the tags specified in the domain context. The request parameters are shown in Table~\ref{tab:screen_find_request} and the response parameters are shown in Table~\ref{tab:screen_find_response}.

>>>>

\usepackage{inputenc}
\usepackage{lastpage}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage[pdfborder={0 0 0}]{hyperref}		% turn on when latex is used (not miktec)
\usepackage{url} % LEO: urls \url{}
\usepackage{verbatim} % code and comment
\usepackage{longtable}
\usepackage{xspace}   % whitespace after a macro if no punctuation after the macro
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable}
\usepackage{array}
\usepackage{amssymb}

% This helps to get hyphenation in typewriter font (\texttt)
\usepackage[htt]{hyphenat}

\parindent0pt

\newcommand\deliverableNumber{D5.2.2}
\newcommand\deliverableTitle{Prototype Semantic Catalogue for Screen-Flow Gadgets and Back-End Services}
\newcommand\deliverableTitleShort{FAST Catalogue}
\newcommand\workpackageNumber{5}
\newcommand\workpackageTitle{Semantic catalogue of screen-flow resources and back-end Web Services}
\newcommand\authorOne{Ismael Rivera, NUIG}
\newcommand\authorTwo{Author 2}
\newcommand\authorThree{Author 3}
\newcommand\authorFour{Author 4}
\newtheorem{example}{\emph{Example}}

@@

%\begin{minipage}[p]{15cm}
	\begin{center}
		\includegraphics{images/FAST_logo}\\
		\vspace{1cm}
		{\LARGE{\sffamily \emph{FAST AND ADVANCED STORYBOARD TOOLS}}}\\
		\vspace{0.5cm}
		{\LARGE \sffamily \emph{FP7-ICT-2007-1-216048}}\\
		\vspace{0.5cm}
		{\LARGE \sffamily \emph{http://fast.morfeo-project.eu}}\\
		\vspace{4cm}
		{\LARGE \sffamily \textbf{Deliverable \deliverableNumber}}\\
		\vspace{0.5cm}
		{\LARGE \sffamily \textbf{\deliverableTitle}}\\
		\vspace{2cm}
		{\large \sffamily \authorOne}\\
		\vspace{0.5cm}
		\vfill
		{\large \sffamily Date: 19/02/2010}\\
		\vspace{1cm}
		{\sffamily FAST is partially funded by the E.C. (grant code: FP7-ICT-2007-1-216048).}

@@

\begin{small}
\begin{tabular}{|l|l|l|p{7.5cm}|}
\hline
\rowcolor{fast@lightgrey}\textcolor{white}{\textbf{Rev. No.}} &
                         \textcolor{white}{\textbf{Date}} &
                         \textcolor{white}{\textbf{Author (Partner)}} &
                         \textcolor{white}{\textbf{Change description}}\\ \hline
1.0 & 20/02/2009 & Ismael Rivera (NUIG) & First version of the deliverable \\ \hline
2.0 & 19/02/2010 & Ismael Rivera (NUIG) & Second version of the deliverable \\ \hline
\end{tabular}
\end{small}

@@

The present deliverable is an appendix to the software deliverable of the semantic catalogue prototype. It includes references to other deliverables where the reader can find further information about the catalogue.

@@

\begin{small}
\begin{tabular}
	{| >{\columncolor{fast@lightgrey}}p{3.25cm}|p{1.4cm}|p{3.2cm}|p{1.6cm}|p{3.37cm}|}
	\hline
	\textcolor{white}{\textbf{Delivery data}} & {\textbf{Due date}} & {27/02/2010} & {\textbf{Submitted}} & {27/02/2010}\\ \hline
	\textcolor{white}{\textbf{Status}} & \multicolumn{2}{l|}{} & \multicolumn{2}{l|}{final}\\ \hline
	\textcolor{white}{\textbf{Dissemination Level}} & \multicolumn{4}{l|}{Public $\boxtimes$ / Consortium $\square$}\\ \hline
	\textcolor{white}{\textbf{Short description of contents}} & \multicolumn{4}{p{10.85cm}|}{This deliverable is the software prototype of the semantic catalogue. This document is just an appendix to it.}\\ \hline
	\textcolor{white}{\textbf{Authors}} & \multicolumn{4}{l|}{\authorOne}\\
%	{} & \multicolumn{4}{l|}{\authorTwo}\\ 
%	{} & \multicolumn{4}{l|}{\authorOne}\\ 
%	{} & \multicolumn{4}{l|}{\authorOne}\\
  \hline
	\textcolor{white}{\textbf{Deliverable Owner}} & \multicolumn{2}{l|}{\authorOne} & \textbf{email} & {ismael.rivera@deri.org} \\ \cline{4-5}
	\textcolor{white}{\textbf{(Partner)}} & \multicolumn{2}{l|}{} & \textbf{phone} & {+353 91 495338} \\ \hline
	\textcolor{white}{\textbf{Keywords}} & \multicolumn{4}{p{10.85cm}|}{FAST, semantic catalogue, gadget catalogue, RDF store}\\ \hline
\end{tabular}
\end{small}

@@

@@

\clearpage
\section{Introduction} % (fold)
\label{sec:introduction}
This section starts establishing the goal and scope of the present deliverable, and shows references to other deliverables for further information.

@@

The semantic catalogue will store and index screen-flow resources and back-end Web services, locate appropriate Web services for users, endow gadgets with functionality based on Service descriptions and resolve mediation problems between gadgets and their back-end services.

This document serves as an appendix to the semantic catalogue deliverable.

@@

This document is not intended to provide any further information regarding the semantic catalogue prototype. For information regarding where the code of the catalogue can be found, installation instructions, system requirements, a overview of the catalogue architecture and a detail API, please read \cite{palaguita2010_usermanual}.

@@

\clearpage
\bibliographystyle{apalike}
\bibliography{fast_d5_2_2}
